# Complaint Analysis

### by Group 4

## Chi-Square Test

Ho = There is no relationship between the categorical variables i.e. they are independent.

H1 = There is relationship between the categorical variables i.e. they are dependent.

Inference: If p-value \< alpha, then Reject Ho; If p-value \> alpha, then Do not reject Ho

```{r,warning=FALSE}
library(readxl)
insurance_complaints <- read_excel("C:/Users/Tanmay/Downloads/insurance complaints.xlsx")
View(insurance_complaints)
data = insurance_complaints
```

### **STATUS vs STATUS**

```{r,warning=FALSE}
status_status = table(data$Status,data$Status)
status_status
chisq.test(status_status)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

### **STATUS vs CONCLUSION**

```{r,warning=FALSE}
status_conclusion = table(data$Conclusion,data$Status)
status_conclusion
chisq.test(status_conclusion)
```

Since the p-value \> alpha , we Do not reject Ho and conclude that they are independent on each other

### **REASON vs REASON**

```{r,warning=FALSE}
reason_reason = table(data$Reason,data$Reason)
reason_reason
chisq.test(reason_reason)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

### **REASON vs COVERAGE**

```{r,warning=FALSE}
reason_coverage = table(data$Reason,data$Coverage)
reason_coverage
chisq.test(reason_coverage)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

### **REASON vs CONCLUSION**

```{r,warning=FALSE}
reason_conclusion = table(data$Reason,data$Conclusion)
reason_conclusion
chisq.test(reason_conclusion)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

### **REASON vs STATUS**

```{r,warning=FALSE}
reason_status = table(data$Reason,data$Status)
reason_status
chisq.test(reason_status)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

### **CONCLUSION vs CONCLUSION**

```{r,warning=FALSE}
concl_concl = table(data$Conclusion,data$Conclusion)
concl_concl
chisq.test(concl_concl)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

### **COVERAGE vs COVERAGE**

```{r,warning=FALSE}
coverage_coverage = table(data$Coverage,data$Coverage)
coverage_coverage
chisq.test(coverage_coverage)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

### **COVERAGE vs CONCLUSION**

```{r,warning=FALSE}
coverage_concl = table(data$Coverage,data$Conclusion)
coverage_concl
chisq.test(coverage_concl)
```

The problem is that you can't have expected frequencies to be zero, because that would throw off the calculation of the chi-squared statistic (we might have zeros in the denominator).

No result

### **COVERAGE vs STATUS**

```{r,warning=FALSE}
coverage_status = table(data$Coverage,data$Status)
coverage_status
chisq.test(coverage_status)
```

Since the p-value \< alpha , we reject Ho and conclude that they are dependent on each other

## **Conclusion**
**The variables 'Status' and 'Conclusion' are independent of each other rest all the variables that we compared are dependent on each other.**